Performing Cluster Analysis on TAD boundaries & Annotations

### 2019-03-24 Scripts/evaluating_pca.Rmd
add clustering by tad

  png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/", 
                       cl, resolution, predictortype, annotation,
                       ".png", sep=""),
      width=11, height=8, units="in", res = 300)
  print({
    autoplot(prcomp(data[,-c(dim(data)[2]-1,dim(data)[2])]),
           data=data,
           #loadings = TRUE,
           label = TRUE, 
           label.size = 3,
           label.repel=T, 
           colour="Cluster",
           shape="Medoid",
           label.show.legend = FALSE) +
    theme_bw()
  })
  dev.off()

@@

>>>>

  png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/cluster_by_annotation/", 
                       cl, resolution, predictortype, annotation,
                       ".png", sep=""),
      width=11, height=8, units="in", res = 300)
  print({
    autoplot(prcomp(data[,-c(dim(data)[2]-1,dim(data)[2])]),
           data=data,
           #loadings = TRUE,
           label = TRUE, 
           label.size = 3,
           label.repel=T, 
           colour="Cluster",
           shape="Medoid",
           label.show.legend = FALSE) +
    theme_bw()
  })
  dev.off()

@@

```{r}
tadclusterplotfunction <- function(cl, resolution, predictortype, cluster){

  if(cluster=="kmedoids"){
    #perform PAM clustering
    clusters <- pam(data, k = pamk.best$nc, diss = FALSE,
                   metric = "manhattan", 
                   #medoids = NULL, 
                   #stand = FALSE, 
                   cluster.only = FALSE,
                   do.swap = TRUE,
                   keep.diss = FALSE,
                   keep.data = FALSE,
                   pamonce = FALSE, 
                   trace.lev = 0)

    data <- data.frame(data)
    data$Cluster <- factor(clusters$clustering)
    data$Medoid <- factor(ifelse(rownames(data) %in% rownames(clusters$medoids), "Center", "Other"),
                          levels=c("Other", "Center"))
  }else{
    clusters <- kmeans(data, centers = pamk.best$nc, nstart = 25, iter.max = 1000)

    data <- data.frame(data)
    data$Cluster <- factor(clusters$cluster)
    data$Medoid <- NA
  }

  data <- data.frame(data)

  png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/cluster_by_tad/", 
                       cl, resolution, predictortype, annotation,
                       ".png", sep=""),
      width=11, height=8, units="in", res = 300)
  print({
    autoplot(prcomp(data[,-c(dim(data)[2]-1,dim(data)[2])]),
             data=data,
             #loadings = TRUE,
             label = FALSE, 
             #label.size = 3,
             #label.repel=T, 
             colour="Cluster",
             #shape="Medoid",
             size=3,
             frame = TRUE, 
             frame.type = 'norm',
             label.show.legend = FALSE) +
      theme_bw()
  })
  dev.off()
